STAT 450 Project: Real Estate

### 2020-03-23 src/2nd_draft.Rmd
typo corrected
Format List

Our goal is to predict mill rates in 2020 in the following 22 municipalities:

- Burnaby
- Coquitlam
- Delta
- Langley - City
- Langley - Township
- Maple Ridge
- Maple Ridge Rural
- New Westminster
- North Vancouver - City
- North Vancouver - Dist
- Pitt Meadows
- Port Coquitlam
- Port Moody
- Richmond
- Surrey
- Vancouver
- White Rock
- West Vancouver
- Bowen Island
- Anmore
- Belcarra
- Lions Bay.

@@

- TaxClass Code in (01,05,06)
- Municipality in Metro Vancouver

@@

There are 1801 missing value in mill rate. 1509 are imputed, and 292 are removed from the data frame. The imputation method is mentioned in appendix.

@@

- Mill rate ("rate": 2016-2019)
- Total Assessment ("assessTotal": 2016-2019)
- Total Land Assessment ("landTotal": 2016 - 2019)
- Total Improvement Assessment ("improvementTotal": 2016 - 2019)
- Total number of properties ("propertyCount")
- Taxclasscode ("TaxClassCode": 01, 05, 06)
- Municipality ("AddressAssessorMunicipalityDesc")
- Year

@@

###Exploratory Analysis

@@

###Linear Model

>>>>

Our goal is to predict mill rates in 2020 in Metro Vancouver.

@@

- TaxClass Code in (01,05,06)
- Municipality in (Burnaby, Coquitlam, Delta, Langley - City, Langley - Township, Maple Ridge, Maple Ridge Rural, New Westminster, North Vancouver - City, North Vancouver - Dist, Pitt Meadows, Port Coquitlam, Port Moody, Richmond, Surrey, Vancouver, White Rock, West Vancouver,  Bowen Island, Anmore, Belcarra, Lions Bay)

@@

There are 1801 missing value in mill rate. 1509 are imputed, and 292 are removed from the data frame. The imputation method is mentioned in **Appendix**.

@@

- Mill rate (rate)
- Total Assessment (assessTotal)
- Total Land Assessment (landTotal)
- Total Improvement Assessment (improvementTotal)
- Total number of properties (propertyCount)
- Taxclasscode (TaxClassCode)
- Municipality (AddressAssessorMunicipalityDesc)
- Year

@@

@@

#### Linear Model
